\textcolor{blue}{Local Maximum Entropy Material Point Method applied to quasi-brittle fracture.}

### 2020-10-09 2020_EFM_MPM_Eigensoftening.tex
symbols

\usepackage{siunitx}
\usepackage[record,% using bib2gls
 symbols, % create list of symbols
 acronym
]{glossaries-extra}

\GlsXtrLoadResources[
  src={symbols}, % data in symbols.bib
  sort-field={name}, % sort by name field
  sort={letter-nocase}, % case-insensitive letter sort
  type=symbols, % put these terms in the symbols list
  field-aliases={unit=symbol}% convert unit key to symbol
]

% Init glossaries
%\usepackage[acronym]{glossaries}
%\makeglossaries

@@

\printglossaries

>>>>

\usepackage{siunitx}
%\usepackage[record,% using bib2gls
% acronym
%]{glossaries-extra}

%\GlsXtrLoadResources[
%  src={symbols}, % data in symbols.bib
%  sort-field={name}, % sort by name field
%  sort={letter-nocase}, % case-insensitive letter sort
%  type=symbols, % put these terms in the symbols list
%  field-aliases={unit=symbol}% convert unit key to symbol
%]

% Init glossaries
\usepackage[acronym]{glossaries}
\makeglossaries

@@

\printglossaries
%\printunsrtglossary[type=symbols,style=alttreegroup,title={List of Symbols}]
